\documentclass[10pt,stdletter,dateno]{newlfm}
\usepackage[frenchb]{babel}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

\widowpenalty=1000
\clubpenalty=1000

\newlfmP{headermarginskip=20pt}
\newlfmP{sigsize=50pt}
\newlfmP{dateskipafter=20pt}
\newlfmP{addrfromphone}
\newlfmP{addrfromemail}
\PhrPhone{Phone}
\PhrEmail{Email}

\namefrom{Thomas Van Gysegem}
\addrfrom{%
    \today\\[10pt]
    Thomas Van Gysegem\\
    46 Rue du Ch\^ene\\
    4350 Momalle, Belgium
}
\phonefrom{Mobile: +32 496 78 60 36}
\emailfrom{thomasvangysegem@gmail.com}

\addrto{%
CATT\\
Innovation Management\\
Linz, Austria}

\greetto{Dear Mrs Krenn,}
\closeline{Yours sincerely,}
\begin{document}
\begin{newlfm}

I am writing to apply for the placement offer 5929 for my third year in Computer Science
at \og Haute \'Ecole de la Province de Li\`ege\fg. I am in my last year of study.
In term of this, I will be awarded a bachelor degree in Industrial computing. My aim is to achieve an internship 
in the field of game development and the placement offer offered by your company would be 
a good preparation for next continuing my studies in that direction.

I practice programming for roughly 7 years. Since then,
I have experienced a lot of different techniques and languages. I also had the opportunity to develop a lot
of different projects in various areas like image processing, real-time processing,
game and website (some of them were developed in a team) but my favourite kind of project is those in relation with game development. 
I am confident that my educational background is in keeping with your requirements.

I will also enjoy the opportunity of visiting Austria which is, as i heard from my friends, 
a wonderfull land with a great historical background and lots of really beautifull landscape.

My greatest desire would be to integrate a motivated development team in the field of video game development as 
this is, in my opinion, the most interesting kind of project. Your placement offer seems to be exactly what I'm looking for.

I am highly motivated, hardworking and reliable, and I would particularly
welcome the opportunity to work in a motivated team in the field of game development.
I am confident that your team will benefit both from my enthusiasm and my abilities.

My institution is providing me with an ERASMUS funding.

I hope you will view my application favorably and I look forward to hearing from you soon.
I can be reached at this email address \href{mailto:thomasvangysegem@gmail.com}{\textcolor{blue}{ThomasVanGysegem@gmail.com}}

\end{newlfm}
\end{document}